### 2013-09-24 Tex/chapters/results.tex
Falsche Formulierung behoben
Komma eingefügt

    the specific heat \(c\) diverges logarithmically for the two dimensional
    Ising model and is nominally \(\alpha = 0\).

@@

    I.e.\ for a given dimension they are independent of the precise lattice

>>>>

    the specific heat \(c\) for the two dimensional Ising model is nominally \(\alpha = 0\),
    because \(c\) diverges logarithmically and not exponentially.

@@

    I.e., for a given dimension they are independent of the precise lattice
